Robots Showing Emotions: Emotion Representation with no bio-inspired Body

### 2016-10-18 JournalInteractionStudies/Rebuttal2.txt

General

Reviewer 1
*****************************************
One sentece to introduce next case study was added at the end of each case study

Reviewer 3
*****************************************
Case study titles were changed:
First Case study: Empirical Emotion Parameters
Second Case Study: Addition of Context
Third Case Study: Literature Emotional Parameters

### 2016-10-18 JournalInteractionStudies/Parts/case_studies.tex
Addition of todos in the files, addition of a Rebuttal2.txt to start writing changes done in the text and make the rebuttal to the Editors.

%TODO add some information about the relationship among all the case studies
\begin{figure}
	\centering
	\includegraphics[width=0.75\textwidth]{./Images/ExampleMovement.png}
	\caption{Example of the features used in all case studies. $x$ represents the displacement in meters, $\omega$ is the angular velocity ($rad/s$) and $\theta$ the oscillation of the body around its center ($rad$). The upper sequence depicts a movement based only on linear velocity, while the bottom one shows a sequence with angular and linear movement.}
	\label{fig:features}
\end{figure} 
%%%%%%%%%%%%%%%%%%%%%
\section{First Case Study}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%
Each group of participants was exposed to three rounds, in each of which the robot was performing a different emotion expression. The sequence of rounds was generated randomly without repeating any emotion in the same sequence. The subjects were asked to mark which emotion-related term that best described what they believed the robot was trying to convey, selecting among a set of nine possible options: anger, curiosity, disgust, embarrassment, fear, happiness, sadness, neutral, and pride. It was also added the option to answer: ''Unknown''. Although these ten options were enlisted, just the first eight emotions were implemented. To avoid that spectators could be influenced by previous trials, different emotions were shown to each group.\\

@@

\begin{figure}
	\centering
	\includegraphics[width=0.7\textwidth]{./Images/FirstCase.png} 
	\caption{First case study setup.}
	\label{fig:setup}
\end{figure}  
%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%

@@

It was decided to follow an empirical design for this case study, consisting in taking into account the features that could be changed in the robot base and in composing them to express some basic emotions. The first implementations where tested and tuned basing on the emotions perceived by the researchers from the robot's movement.\\
The features that could easily be perceived by the observer are summarized in table~\ref{table:features}, and each selected feature is described here below:

@@

	\item \textit{Body Rotation Amplitude} is the maximum  rotation angle around its center that the robot base can reach during the linear movement (it is a holonomic base); it could be: ''none`` ($0$) rad, ''small`` ($0.1$) rad, ''medium`` ($0.3$) rad, ''large`` ($0.5$) rad, and ''huge`` ($0.7$) rad.
\begin{table}[tbh]
\begin{center}
\small
\caption{Features that were presented to the audience, and their values. Embarr. is Embarrassment and Asy. is Asymmetric.}
\label{table:features}
\begin{tabular}{|p{1.5 cm}|p{1.5 cm}|c|p{1.5 cm}|p{1.6 cm}|p{1.6 cm}|m{1.5 cm}|}
\hline 
\textbf{Emotion} & \textbf{Speed} & \textbf{Front/Back} & \textbf{Shoulder} & \textbf{Shoulder Amplitude} & \textbf{Angular Velocity} & \textbf{Body Rotation Amplitude} \\ 
\hline
Anger & Fast & No & Asy. & Medium & None & Very Small \\
\hline
Sadness & Very Slow & Yes-1 & Close-2 & None & Slow & Small \\
\hline
Fear & Normal Slow & Yes-2 & Close-2 + Asy. & Small & None & None \\ 
\hline
%Fear 2 & Slow & Yes-2 & Close-2 + Asymmetric & Small & None & Small \\
%\hline
Embarr. & Slow & No & Asy. & Large & Slow & Small \\
\hline
Happiness & Fast & No & Asy. & Medium & Fast & Small \\
\hline
Disgust & Slow & No & Few Asy. & Small & None & Very Small \\
\hline
Curiosity & Normal & No & Asy. & Medium & Slow & Large \\
\hline
Neutral & Normal & No & Asy. & Medium & None & None \\
\hline
\end{tabular}
\end{center}
\vspace{-0.5cm}
\end{table} 
%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Experimental Setup}

@@

Table~\ref{table:results_1} shows the results obtained in the first case study. 
\begin{table}[tbh]
\caption{Answers obtained the first case study. On each row is the emotion that was intended to express, and on the columns the reported emotions.
.}
\small
\label{table:results_1}
\centering
\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|}
\hline
\backslashbox{Presented}{Reported} & 
\rotatebox{90}{\textbf{Anger}}&
\rotatebox{90}{\textbf{Curiosity}}&
\rotatebox{90}{\textbf{Disgust}}&
\rotatebox{90}{\textbf{Embarr.}}&
\rotatebox{90}{\textbf{Fear}}&
\rotatebox{90}{\textbf{Happiness}}&
\rotatebox{90}{\textbf{Neutral}}&
\rotatebox{90}{\textbf{Pride}}&
\rotatebox{90}{\textbf{Sadness}}&
\rotatebox{90}{\textbf{Unk.}}&
\rotatebox{90}{\textbf{Tot.}}&
\rotatebox{90}{\textbf{Percentage}}\\
\hline
Anger &23 &11 &3 &4 &7 &6 &1 &0 &0 &4 &59&38.98\%\\
\hline
Curiosity &2 &9 &3 &9 &2 &3 &2 &8 &3 &0 &41&21.95\%\\
\hline
Disgust& 1 & 11& 1& 3& 7& 3& 6& 8& 5& 1& 46&2.17\%\\
\hline
Embarr. & 3& 11& 0& 8& 9& 3& 0& 4& 2& 1& 41&19.51\%\\
\hline
Fear & 3& 29& 5& 25& 22& 2& 2& 0& 2& 2& 92&22.82\%\\
\hline
Happiness & 15& 4& 0& 2& 3& 28& 4& 4& 2& 1& 63&44.44\%\\
\hline
Neutral & 5& 0& 1& 1& 0& 1& 0& 3& 2& 0& 13&0\%\\
\hline
Sadness & 4& 5& 1& 11& 13& 0& 2& 3& 7& 0& 46&23.81\%\\
\hline
\end{tabular}
\end{table}
Table~\ref{table:results_1} shows that the best emotion perceived was Happiness and the worst one Disgust, with 44\% and 2\% respectively of accuracy. Moreover, some movements were designed to convey a specific emotion, but a different emotion was perceived. For example the intended Sadness was identified by 14\% of subjects exposed to it, while 25.5\% perceived it as Fear. The neutral behaviour was not much considered, possibly because people, in this setting, expected to see something specific, not a neutral movement. To analyse whether each emotional expression was misinterpreted with others a Fisher's exact test was applied for each possible combination of emotions implemented. Additionally, a Holm-Bonferroni correction was applied for multiple comparisons to get better p-value estimation. 
The results showed that people perceived the following implementations as similar, having a $p-value>0.05$: curiosity-disgust, curiosity-embarrassment, curiosity-sadness, disgust-embarrassment, disgust-sadness, embarrassment-fear, embarrassment-sadness, and fear-sadness.

@@

\begin{table}
\begin{center}
\small
\caption{Example of table compiled for each emotion on the subjects that have been presented each emotion (here Happiness).}
\label{table:singleEmotion}
\begin{tabular}{|c|c|c|}
\hline 
\backslashbox{Presented}{Reported}&Happiness&Other\\
\hline 
Happiness&28&4\\
\hline 
Other&30&96\\
\hline
\end{tabular}
\end{center}
%\vspace{-0.5cm}
\end{table}
For each of these tables the classification accuracy and the no-information rate (NIR), i.e. the accuracy that had been obtained by random selection, have been computed with the R package CARET~\cite{caret}.
The results show that some implementations of emotion expression (i.e., Anger ($p-value=1e-3$) and Happiness ($p-value=2.8e-5$)) have been recognized by the respective panels, while others are not.
%%%%%%%%%%%%%%%%%%%%%
\section{Second Case Study}
Since the results of the first case study showed that the recognition of most of the designed emotions was still quite poor, it was decided to try again with the same emotions, but this time a context to the emotional state of the robot was provided by playing a little scene. This is motivated by the fact that that emotions are triggered by stimuli~\cite{Plutchik2001,cacioppo2000handbook}.
%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%

@@

A little scene was created for each emotion to give a context to the participants. The procedure and questionnaire were the same as the one adopted for the first case. However, it was added a variant of the Fear emotion (Fear2), in which the robot finishes its trajectory far from the person. As done in the first case, each group was exposed to three emotions and the sequence presented to each group was different to eliminate the chance to influence other groups. The sequences were generated randomly and without repeating an emotion in a sequence.\\

@@

\begin{figure}
	\centering
	\includegraphics[width=0.6\textwidth]{./Images/SecondCase.png} 
	\caption{Setup of the second case study.}
	\label{fig:setup2}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Study}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{table}[tbh]
\caption{Answers obtained in the second case studies. On each row is the emotion that was intended to express, and on the columns the reported emotions.}
\small
\label{table:results_2}
\centering
\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|}
\hline
\backslashbox{Presented}{Reported} & 
\rotatebox{90}{\textbf{Anger}}&
\rotatebox{90}{\textbf{Curiosity}}&
\rotatebox{90}{\textbf{Disgust}}&
\rotatebox{90}{\textbf{Embarr.}}&
\rotatebox{90}{\textbf{Fear}}&
\rotatebox{90}{\textbf{Happiness}}&
\rotatebox{90}{\textbf{Neutral}}&
\rotatebox{90}{\textbf{Pride}}&
\rotatebox{90}{\textbf{Sadness}}&
\rotatebox{90}{\textbf{Unk.}}&
\rotatebox{90}{\textbf{Tot.}}&
\rotatebox{90}{\textbf{Percentage}}\\
\hline
Anger &41 &1 &2 &0 &6 &9 &0 &2 &0 &1 &62&66.13\%\\
\hline
Curiosity &8 &38 &0 &3 &0 &4 &1 &1 &1 &4 &60&63.33\%\\
\hline
Disgust& 6& 2& 5& 4& 3& 0& 4& 7& 4& 3& 38&13.16\%\\
\hline
Embarr. & 7& 2& 1& 4& 12& 0& 0& 1& 10& 0& 37&10.81\%\\
\hline
Fear & 0& 13& 0& 17& 10& 6& 0& 0& 0& 0& 46&21.74\%\\
\hline
Fear2 & 3& 0& 5& 5& 35& 0& 1& 0& 2& 0& 51&68.63\%\\
\hline
Happiness & 0& 1& 0& 0& 5& 55& 1& 0& 0& 1& 63&87.30\%\\
\hline
Neutral & 1& 3& 2& 5& 7& 9& 5& 5& 1& 1& 39&12.82\%\\
\hline
Sadness & 0& 4& 2& 22& 14& 0& 2& 3& 15& 1& 63&23.81\%\\
\hline
\end{tabular}
\end{table}
In the second case study, the results were considerably better, where four out of the nine showed emotions had a percentage of recognition higher than 60\% (Anger, Happiness, Curiosity and Fear2). Another important point to highlight is that Sadness, Fear and Embarrassment were still perceived as different emotions. As it was done for the first case study, a Fisher's exact test and Holm-Bonferroni correction were applied for each possible combination of implemented emotions. The results suggest that no implementation was considered as similar to others by the participants, since for all we have $p-value<\alpha$.  Comparing the percentage from both cases, it is possible to see that giving information about the context that produces the current emotional state of the robot improves its recognition. However, if the conveyed emotion does not match the scene, the audience does not recognize it. This shows that even giving information about the situation, and using a human actor to provide the context, people could not recognize the emotion if the correct features are not exploited. To verify this, it was done a comparison between the results obtained for each emotion in both cases doing a Fisher's exact test. The results suggest that implementations of Disgust ($p=0.088$), Fear ($p=0.206$) and Sadness ($p=0.269$) are perceived as the same in both cases. This would suggest that the combination of stimuli (scene + actor) and correct robot's movements are necessary to the correct emotional interpretation. However with the adopted setup, it was impossible to determine which factor had more relevance.
%%%%%%%%%%%%%%%%%%%%%
\section{Third Case Study}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Experimental setup}

@@

In order to study the influence that could be generated by the given list of emotions to the participants, it was used an open questionnaire that did not list any emotion, but rather had a space where participants could write a term to answer the question: "\textit{What emotion the robot has expressed?}".
The setup used in this case study is depicted in the Figure~\ref{fig:setup2}.
\begin{figure}
	\centering
	\includegraphics[width=0.6\textwidth]{./Images/ThirdCase.png} 
	\caption{Setup of the third case study.}
	\label{fig:setup2} %TODO check whether it is the correct setup. Yes, it was two meters and with some boxes to not let the participants move over the robots path. OK, just because the number did not match (setup2 for the 3rd case study)
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Emotion Descriptions} 
Due to the scarce literature about emotional parameters in robotics, the selection of the parameters for the implemented emotions were made following the literature in human emotion projection~\cite{Nadia2013, Crane2013}.
Generally speaking, these works use the Laban's notation to code their findings, which leaves to the designer (and the reader) their specific interpretation.\\

@@

	\item \textit{\textit{Happiness}:} as in \textit{Anger}, for the first $50mm$ the velocity was $500mm/sec$, then it went down to $400mm/sec$ for another $50mm$, and then up again to $800mm/sec$ for the rest of the movement. 
	An oscillation between [0.26, -0.26] radians with an angular velocity of $3rad/sec$ was also added.

@@

	\item \textit{Content:} the velocity was $150mm/sec$ for the first $200mm$, then $300mm/sec$ for the rest. The maximum and minimum angle of oscillation were [0.175, -0.175] with angular velocity of $0.17rad/sec$

@@

%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Study}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%
From the open questionnaire, different terms to describe both emotions and mental states were obtained. In table~\ref{table:open_questionnaire} are reported the results. In order to reduce the quantity of words, words that have a similar meaning were grouped, for example words as \textit{Fear}, \textit{Terror}, \textit{Scared}, and \textit{Worried} were grouped under the label \textit{Fear}. Also, three out of four emotions (\textit{Anger}, \textit{Happiness} and \textit{Sadness}) were at least once listed correctly. \textit{Sadness} and \textit{Content} were mostly perceived as \textit{Fear}, being written 31\% and 28\% of the time for each of these two emotions respectively.\\

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}
\centering
		\caption{Results obtained from the open questionnaire.}
		\label{table:open_questionnaire}
		\small
			\begin{tabular}{|c|c|c|c|c|c|}
				\hline
					\backslashbox{Presented}{Reported}&\textit{Anger}&\textit{Happiness}&\textit{Sadness}&\textit{Content}&Total\\
				\hline
					\textit{Anger}& 3&6&7&5&21\\
				\hline
					\textit{Happiness}&12& 18&0&6&36\\
				\hline
					\textit{Sadness}&0&0& 8&3&11\\
				\hline
					\textit{Content}&2&0&0& 0&2\\
				\hline
					\textit{Fear}&4&5&14&13&36\\
				\hline
					\textit{Tiredness}&1&0&1&1&3\\
				\hline
					\textit{Cold}&2&0&2&1&5\\
				\hline
					\textit{Shyness}&1&0&4&4&9\\
				\hline
					\textit{Agitated}&4&1&0&0&5\\
				\hline
					\textit{Power}&4&1&0&0&5\\
				\hline
					\textit{Hurry}&0&1&0&0&1\\
				\hline
					\textit{Looking for something}&1&0&1&0&2\\
				\hline
					\textit{He wants something}&1&0&1&0&2\\
				\hline
					\textit{Tenderness}&1&0&1&2&4\\
				\hline
					\textit{Uncertainty}&1&2&0&0&3\\
				\hline
					\textit{Enthusiasm}&1&0&0&0&1\\
				\hline
					\textit{Sympathy}&1&0&2&4&7\\
				\hline
					\textit{Curiosity}&1&2&3&3&9\\
				\hline
					\textit{Shame}&0&0&0&1&1\\
				\hline
					\textit{Nothing}&1&2&1&0&4\\
				\hline
					\textit{Vanity}&1&0&0&0&1\\
				\hline
					\textit{Obedience}&0&0&0&1&1\\
				\hline
					\textit{Total}&43&38&44&46&171\\
				\hline
			\end{tabular}
\end{table}

@@

%%%%%%%%%%%%%%%%%%%%%%
\section{Fourth Case Study}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.60\textwidth]{./Images/FourthCase.png} 
	\caption{Environment setup for the fourth case study. The crosses symbolize the two possible starting points.}
	\label{fig:setup_fourth}
\end{figure} 
%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Emotion Descriptions} 
The selected emotion descriptions could be seen in Table~\ref{table:features_2}
\begin{table}[tbh]

>>>>

%TODO add some information about the relationship among all the case studies
\begin{figure}[h]
	\centering
	\includegraphics[width=0.75\textwidth]{./Images/ExampleMovement.png}
	\caption{Example of the features used in all case studies. $x$ represents the displacement in meters, $\omega$ is the angular velocity ($rad/s$) and $\theta$ the oscillation of the body around its center ($rad$). The upper sequence depicts a movement based only on linear velocity, while the bottom one shows a sequence with angular and linear movement.}
	\label{fig:features}
\end{figure} 
%%%%%%%%%%%%%%%%%%%%%

\section{First Case Study: Empirical Emotion Parameters}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Design}

Each group of participants was exposed to three rounds, in each of which the robot was performing a different emotion expression. The sequence of rounds was generated randomly without repeating any emotion in the same sequence. The subjects were asked to mark which emotion-related term that best described what they believed the robot was trying to convey, selecting among a set of nine possible options: anger, curiosity, disgust, embarrassment, fear, happiness, sadness, neutral, and pride. It was also added the option to answer: ''Unknown''. Although these ten options were enlisted, just the first eight emotions were implemented. To avoid that spectators could be influenced by previous trials, different emotions were shown to each group.

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=0.7\textwidth]{./Images/FirstCase.png} 
	\caption{First case study setup.}
	\label{fig:setup}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%

@@

It was decided to follow an empirical design for this case study, consisting in taking into account the features that could be changed in the robot base and in composing them to express some basic emotions. The first implementations where tested and tuned basing on the emotions perceived by the researchers from the robot's movement.\\
The features that could easily be perceived by the observer are summarized in table~\ref{table:features}, and each selected feature is described here below:

@@

	\item \textit{Body Rotation Amplitude} is the maximum  rotation angle around its center that the robot base can reach during the linear movement (it is a holonomic base); it could be: ''none`` ($0$) rad, ''small`` ($0.1$) rad, ''medium`` ($0.3$) rad, ''large`` ($0.5$) rad, and ''huge`` ($0.7$) rad.
\end{itemize}

\begin{table}[tbh]
\begin{center}
\small
\caption{Features that were presented to the audience, and their values. Embarr. is Embarrassment and Asy. is Asymmetric.}
\label{table:features}
\begin{tabular}{|p{1.5 cm}|p{1.5 cm}|c|p{1.5 cm}|p{1.6 cm}|p{1.6 cm}|m{1.5 cm}|}
\hline 
\textbf{Emotion} & \textbf{Speed} & \textbf{Front/Back} & \textbf{Shoulder} & \textbf{Shoulder Amplitude} & \textbf{Angular Velocity} & \textbf{Body Rotation Amplitude} \\ 
\hline
Anger & Fast & No & Asy. & Medium & None & Very Small \\
\hline
Sadness & Very Slow & Yes-1 & Close-2 & None & Slow & Small \\
\hline
Fear & Normal Slow & Yes-2 & Close-2 + Asy. & Small & None & None \\ 
\hline
%Fear 2 & Slow & Yes-2 & Close-2 + Asymmetric & Small & None & Small \\
%\hline
Embarr. & Slow & No & Asy. & Large & Slow & Small \\
\hline
Happiness & Fast & No & Asy. & Medium & Fast & Small \\
\hline
Disgust & Slow & No & Few Asy. & Small & None & Very Small \\
\hline
Curiosity & Normal & No & Asy. & Medium & Slow & Large \\
\hline
Neutral & Normal & No & Asy. & Medium & None & None \\
\hline
\end{tabular}
\end{center}
\vspace{-0.5cm}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Experimental Setup}

@@

Table~\ref{table:results_1} shows the results obtained in the first case study. 
\begin{table}[tbh]
\caption{Answers obtained the first case study. On each row is the emotion that was intended to express, and on the columns the reported emotions.
.}
\small
\label{table:results_1}
\centering
\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|}
\hline
\backslashbox{Presented}{Reported} & 
\rotatebox{90}{\textbf{Anger}}&
\rotatebox{90}{\textbf{Curiosity}}&
\rotatebox{90}{\textbf{Disgust}}&
\rotatebox{90}{\textbf{Embarr.}}&
\rotatebox{90}{\textbf{Fear}}&
\rotatebox{90}{\textbf{Happiness}}&
\rotatebox{90}{\textbf{Neutral}}&
\rotatebox{90}{\textbf{Pride}}&
\rotatebox{90}{\textbf{Sadness}}&
\rotatebox{90}{\textbf{Unk.}}&
\rotatebox{90}{\textbf{Tot.}}&
\rotatebox{90}{\textbf{Percentage}}\\
\hline
Anger &23 &11 &3 &4 &7 &6 &1 &0 &0 &4 &59&38.98\%\\
\hline
Curiosity &2 &9 &3 &9 &2 &3 &2 &8 &3 &0 &41&21.95\%\\
\hline
Disgust& 1 & 11& 1& 3& 7& 3& 6& 8& 5& 1& 46&2.17\%\\
\hline
Embarr. & 3& 11& 0& 8& 9& 3& 0& 4& 2& 1& 41&19.51\%\\
\hline
Fear & 3& 29& 5& 25& 22& 2& 2& 0& 2& 2& 92&22.82\%\\
\hline
Happiness & 15& 4& 0& 2& 3& 28& 4& 4& 2& 1& 63&44.44\%\\
\hline
Neutral & 5& 0& 1& 1& 0& 1& 0& 3& 2& 0& 13&0\%\\
\hline
Sadness & 4& 5& 1& 11& 13& 0& 2& 3& 7& 0& 46&23.81\%\\
\hline
\end{tabular}
\end{table}

Table~\ref{table:results_1} shows that the best emotion perceived was Happiness and the worst one Disgust, with 44\% and 2\% respectively of accuracy. Moreover, some movements were designed to convey a specific emotion, but a different emotion was perceived. For example the intended Sadness was identified by 14\% of subjects exposed to it, while 25.5\% perceived it as Fear. The neutral behaviour was not much considered, possibly because people, in this setting, expected to see something specific, not a neutral movement. To analyse whether each emotional expression was misinterpreted with others a Fisher's exact test was applied for each possible combination of emotions implemented. Additionally, a Holm-Bonferroni correction was applied for multiple comparisons to get better p-value estimation. 
The results showed that people perceived the following implementations as similar, having a $p-value>0.05$: curiosity-disgust, curiosity-embarrassment, curiosity-sadness, disgust-embarrassment, disgust-sadness, embarrassment-fear, embarrassment-sadness, and fear-sadness.

@@

\begin{table}[h]
\begin{center}
\small
\caption{Example of table compiled for each emotion on the subjects that have been presented each emotion (here Happiness).}
\label{table:singleEmotion}
\begin{tabular}{|c|c|c|}
\hline 
\backslashbox{Presented}{Reported}&Happiness&Other\\
\hline 
Happiness&28&4\\
\hline 
Other&30&96\\
\hline
\end{tabular}
\end{center}
%\vspace{-0.5cm}
\end{table}

For each of these tables the classification accuracy and the no-information rate (NIR), i.e. the accuracy that had been obtained by random selection, have been computed with the R package CARET~\cite{caret}.
The results show that some implementations of emotion expression (i.e., Anger ($p-value=1e-3$) and Happiness ($p-value=2.8e-5$)) have been recognized by the respective panels, while others are not.

The result shows that it is possible to convey some emotions using just movement and a non-bio-inspired embodiment. Moreover, showing emotional states in a context that puts in evidence the stimulus that produced them (as it would happen in a real application) might improve the perception of the emotions, as it is known also for human-human relationships, and this is study in the second case study.

%%%%%%%%%%%%%%%%%%%%%
\section{Second Case Study: Addition of Context}

Since the results of the first case study showed that the recognition of most of the designed emotions was still quite poor, it was decided to try again with the same emotions, but this time a context to the emotional state of the robot was provided by playing a little scene. This is motivated by the fact that that emotions are triggered by stimuli~\cite{Plutchik2001,cacioppo2000handbook}.
%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%

@@

A little scene was created for each emotion to give a context to the participants. The procedure and questionnaire were the same as the one adopted for the first case. However, it was added a variant of the Fear emotion (Fear2), in which the robot finishes its trajectory far from the person. As done in the first case, each group was exposed to three emotions and the sequence presented to each group was different to eliminate the chance to influence other groups. The sequences were generated randomly and without repeating an emotion in a sequence.

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=0.6\textwidth]{./Images/SecondCase.png} 
	\caption{Setup of the second case study.}
	\label{fig:setup2}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Study}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Results}

@@

\begin{table}[tbh]
\caption{Answers obtained in the second case studies. On each row is the emotion that was intended to express, and on the columns the reported emotions.}
\small
\label{table:results_2}
\centering
\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|}
\hline
\backslashbox{Presented}{Reported} & 
\rotatebox{90}{\textbf{Anger}}&
\rotatebox{90}{\textbf{Curiosity}}&
\rotatebox{90}{\textbf{Disgust}}&
\rotatebox{90}{\textbf{Embarr.}}&
\rotatebox{90}{\textbf{Fear}}&
\rotatebox{90}{\textbf{Happiness}}&
\rotatebox{90}{\textbf{Neutral}}&
\rotatebox{90}{\textbf{Pride}}&
\rotatebox{90}{\textbf{Sadness}}&
\rotatebox{90}{\textbf{Unk.}}&
\rotatebox{90}{\textbf{Tot.}}&
\rotatebox{90}{\textbf{Percentage}}\\
\hline
Anger &41 &1 &2 &0 &6 &9 &0 &2 &0 &1 &62&66.13\%\\
\hline
Curiosity &8 &38 &0 &3 &0 &4 &1 &1 &1 &4 &60&63.33\%\\
\hline
Disgust& 6& 2& 5& 4& 3& 0& 4& 7& 4& 3& 38&13.16\%\\
\hline
Embarr. & 7& 2& 1& 4& 12& 0& 0& 1& 10& 0& 37&10.81\%\\
\hline
Fear & 0& 13& 0& 17& 10& 6& 0& 0& 0& 0& 46&21.74\%\\
\hline
Fear2 & 3& 0& 5& 5& 35& 0& 1& 0& 2& 0& 51&68.63\%\\
\hline
Happiness & 0& 1& 0& 0& 5& 55& 1& 0& 0& 1& 63&87.30\%\\
\hline
Neutral & 1& 3& 2& 5& 7& 9& 5& 5& 1& 1& 39&12.82\%\\
\hline
Sadness & 0& 4& 2& 22& 14& 0& 2& 3& 15& 1& 63&23.81\%\\
\hline
\end{tabular}
\end{table}

In the second case study, the results were considerably better, where four out of the nine showed emotions had a percentage of recognition higher than 60\% (Anger, Happiness, Curiosity and Fear2). Another important point to highlight is that Sadness, Fear and Embarrassment were still perceived as different emotions. As it was done for the first case study, a Fisher's exact test and Holm-Bonferroni correction were applied for each possible combination of implemented emotions. The results suggest that no implementation was considered as similar to others by the participants, since for all we have $p-value<\alpha$.  Comparing the percentage from both cases, it is possible to see that giving information about the context that produces the current emotional state of the robot improves its recognition. However, if the conveyed emotion does not match the scene, the audience does not recognize it. This shows that even giving information about the situation, and using a human actor to provide the context, people could not recognize the emotion if the correct features are not exploited. To verify this, it was done a comparison between the results obtained for each emotion in both cases doing a Fisher's exact test. The results suggest that implementations of Disgust ($p=0.088$), Fear ($p=0.206$) and Sadness ($p=0.269$) are perceived as the same in both cases. This would suggest that the combination of stimuli (scene + actor) and correct robot's movements are necessary to the correct emotional interpretation. This opens the question about the influence that could have the human actor and the scene on the recognition rate. Although the study of their influence could be beneficial, it was decided to continue the studies on the values that could be used to express emotions. Therefore it was devise a third case study that uses values informed in the literature.

%%%%%%%%%%%%%%%%%%%%%
\section{Third Case Study: Literature Emotional Parameters}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Experimental setup}

@@

In order to study the influence that could be generated by the given list of emotions to the participants, it was used an open questionnaire that did not list any emotion, but rather had a space where participants could write a term to answer the question: "\textit{What emotion the robot has expressed?}".
The setup used in this case study is depicted in the Figure~\ref{fig:setup2}.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.6\textwidth]{./Images/ThirdCase.png} 
	\caption{Setup of the third case study.}
	\label{fig:setup2} 
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Emotion Descriptions}

Due to the scarce literature about emotional parameters in robotics, the selection of the parameters for the implemented emotions were made following the literature in human emotion projection~\cite{Nadia2013, Crane2013}.
Generally speaking, these works use the Laban's notation to code their findings, which leaves to the designer (and the reader) their specific interpretation.

@@

	\item \textit{\textit{Happiness}:} as in \textit{Anger}, for the first $50mm$ the velocity was $500mm/sec$, then it went down to $400mm/sec$ for another $50mm$, and then up again to $800mm/sec$ for the rest of the movement. 
	An oscillation between [0.26, -0.26] radians with an angular velocity of $3rad/sec$ was also added.

@@

	\item \textit{Content:} the velocity was $150mm/sec$ for the first $200mm$, then $300mm/sec$ for the rest. The maximum and minimum angle of oscillation were [0.175, -0.175] with angular velocity of $0.17rad/sec$
\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Study}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Results}

From the open questionnaire, different terms to describe both emotions and mental states were obtained. In table~\ref{table:open_questionnaire} are reported the results. In order to reduce the quantity of words, words that have a similar meaning were grouped, for example words as \textit{Fear}, \textit{Terror}, \textit{Scared}, and \textit{Worried} were grouped under the label \textit{Fear}. Also, three out of four emotions (\textit{Anger}, \textit{Happiness} and \textit{Sadness}) were at least once listed correctly. \textit{Sadness} and \textit{Content} were mostly perceived as \textit{Fear}, being written 31\% and 28\% of the time for each of these two emotions respectively.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[h]
\centering
		\caption{Results obtained from the open questionnaire.}
		\label{table:open_questionnaire}
		\small
			\begin{tabular}{|c|c|c|c|c|c|}
				\hline
					\backslashbox{Presented}{Reported}&\textit{Anger}&\textit{Happiness}&\textit{Sadness}&\textit{Content}&Total\\
				\hline
					\textit{Anger}& 3&6&7&5&21\\
				\hline
					\textit{Happiness}&12& 18&0&6&36\\
				\hline
					\textit{Sadness}&0&0& 8&3&11\\
				\hline
					\textit{Content}&2&0&0& 0&2\\
				\hline
					\textit{Fear}&4&5&14&13&36\\
				\hline
					\textit{Tiredness}&1&0&1&1&3\\
				\hline
					\textit{Cold}&2&0&2&1&5\\
				\hline
					\textit{Shyness}&1&0&4&4&9\\
				\hline
					\textit{Agitated}&4&1&0&0&5\\
				\hline
					\textit{Power}&4&1&0&0&5\\
				\hline
					\textit{Hurry}&0&1&0&0&1\\
				\hline
					\textit{Looking for something}&1&0&1&0&2\\
				\hline
					\textit{He wants something}&1&0&1&0&2\\
				\hline
					\textit{Tenderness}&1&0&1&2&4\\
				\hline
					\textit{Uncertainty}&1&2&0&0&3\\
				\hline
					\textit{Enthusiasm}&1&0&0&0&1\\
				\hline
					\textit{Sympathy}&1&0&2&4&7\\
				\hline
					\textit{Curiosity}&1&2&3&3&9\\
				\hline
					\textit{Shame}&0&0&0&1&1\\
				\hline
					\textit{Nothing}&1&2&1&0&4\\
				\hline
					\textit{Vanity}&1&0&0&0&1\\
				\hline
					\textit{Obedience}&0&0&0&1&1\\
				\hline
					\textit{Total}&43&38&44&46&171\\
				\hline
			\end{tabular}
\end{table}

@@

%TODO write a sentence explaining the results and justying why the experiment and cross validation

%%%%%%%%%%%%%%%%%%%%%%
\section{Fourth Case Study: Experiment Cross-Validation}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=0.60\textwidth]{./Images/FourthCase.png} 
	\caption{Environment setup for the fourth case study. The crosses symbolize the two possible starting points.}
	\label{fig:setup_fourth}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Emotion Descriptions}
